%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\newif\ifenglish
\englishtrue    %COMMENT LINE TO SWITCH FROM ENGLISH TO DANISH


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{red}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Emilio Martin}{Lundgaard Lopez}
%\title{Resumé title}                               % optional, remove / comment the line if not wanted
\address{Markusgade 1, 2tv.}{(9000) Aalborg}{Danmark}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{9399-3436}                   % optional, remove / comment the line if not wanted
%\phone[fixed]{+2~(345)~678~901}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{emilio@lundgaardlopez.com}                               % optional, remove / comment the line if not wanted
\homepage{emilio.lundgaardlopez.com}                         % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{Lyngsoe Systems Denmark}{Lyngsø Allé 3\\9600 Aars, Denmark}
\date{}

\ifenglish
\opening{Dear Sir or Madam,}
\else
\fi

\ifenglish
\closing{Kind regards,}
\else
\closing{Med venlig hilsen,}
\fi

\ifenglish
\enclosure[Attached]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
\else
\fi

\makelettertitle

\ifenglish
\textbf{Professional software developer with innovative ideas}\\
\else
\textbf{Front-end-udvikler med innovative ideer}\\
\fi

\ifenglish
I am from Argentina and have a Computer Science education from the National University of Rosario, Argentina. I am married to a Dane and have a 2 months old son and would very much like to apply for the job as Software developer announced at your webpage.\\
\bigskip
My education of Master in Science in Computer Science has a strong theoretical focus, and it provides me with a wide mathematical and logical konwledge base. During the education, I have learned about topics and concepts that have forged my professional image today. I feel it is relevant for this job to have a strong Software Engineering background as well as a university course in Discrete Mathematics, both of which are present in my academical history.\\ 
\bigskip
I worked as a Software Developer in Argentina for a company called Itecnis. At Itecnis, my main goal was to provide consultancy services but worked as a R\& D asset in between calls. Among the projects in which I worked, some of the most importants consisted on working in groups to bring up web products. For example, I helped bringing up a web solution for holding videoconferences online using just a browser. This was done using WebRTC technology, as well as with the use of many frameworks, NodeJs, MySQL and other tools.\\
\bigskip
As mentioned above, I worked as a IT Consultant. The job required me to be very skillful when it came to costumer service. Good communication skills were very important for my development in the company, and I accomplished a good professional relationship with the company's customers, as well as with my colleagues.\\
\bigskip
I encourage you to take a closer look at my characteristics and experience by looking into my Curriculum Vitae, which I have as well attached to the email in which I have sent this letter.\\
\bigskip
I am truly looking forward to hearing from you.
\else
Jeg er fra Argentina og har en Computer Science uddannelse fra universitet i Rosario, Argentina. Jeg er dansk gift og føler nu, at mine danske sprogfærdigheder, er gode nok til at søge et job indenfor mit kompetence felt.\\

I Argentina har jeg arbejdet som IT konsulent, hvor jeg i flere projekter har stået for Front-end udvikling basseret på Javascript og HTML, ligesom jeg under min uddannelse og intership har anvendt det så meget, at jeg uden tøven kan sige, at jeg behersker disse sprog på et avanceret niveau.\\

Når jeg udvikler, tager jeg udgangspunkt i, at jeg selv ønsker at IT systemer har brugervenlige designs, som giver brugerne en god og positiv oplevelse.\\

Efter min Bachelor eksamen, tog jeg et års sabbat fra studierne, for at arbejde som aupair i USA., hvilket har gjort mig meget selvstændig og ansvarsbevidst. Jeg fik et stort indblik i kulturelle forskelle, forbedrede mine sprogkundskaber og fik en masse nye oplevelser, der har modnet mig som menneske.\\

Jeg har siden jeg kom til Danmark, arbejdet hos Fokus Folkeoplysning som rengøringsassistent, ligesom jeg som projekt medarbejder har lavet en ny hjemmeside til dem.\\

Jeg har spansk som modersmål, taler engelsk flydende og mit danske sprogniveau er nu så godt, at jeg føler mig klar til at have et arbejde, hvor jeg skal samarbejde med såvel kollegaer som kunder.\\

Ved at ansætte mig, får i en selvstændig medarbejder, der er opsat på at bevise, at jeg er en dygtig og dedikeret medarbejder, som er vant til at tackle nye problemer og som bidrager til et godt arbejdsmiljø gennem humor og oprigtig interesse for mine omgivelser.\\

Jeg har ikke mulighed for at arbejde fast i København, men jeg kan lægge hjemmekontor til, hvis det er nødvendigt.\\

På vedlagte CV, kan i læse mere om mine tidligere jobs og uddannelse. Jeg vil se frem til en personlig samtale, for at høre mere om den spændende stilling og uddybende fortælle mere om mine faglige og personlige kompetencer til jobbet.
\fi

\makeletterclosing

%\clearpage\end{CJK*}                              % if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly with CJK, though it kills the page numbering by making \lastpage undefined
\end{document}


%% end of file `template.tex'.
